Supplementary material

### 2025-07-06 code/supplementary.Rmd
temp commit for figure update

# stable dataset
readfile_stable <- str_glue("../readfiles/stable/")
fig_path = "../figs/manuscript/"

@@

```{r absnull, fig.cap="Comparison between the two M&V methods in detecting no intervention effect (expressed without absolute calculation) when buildings are subject to baseline change.", fig.height=6, fig.width=12}
#### ABS-NULL ####
rand_eob_S <- df_seq_fs_null_stable %>% 
  filter(seq == "eob") %>% 
  mutate(diff = abs(0 - fs), 
         method = "rand_eob") %>% 
  select(name, method, diff)

@@

df_MW_A %>% 
  mutate(method = as.factor(method), 
         method = recode_factor(method, "conv_diff" = "Conventional", "rand_eob_diff" = "Randomized", "rand_final_diff" = "Randomized\n(24 months)")) %>% 
  ggplot(aes(x = method, y = diff, fill = method)) +
  geom_jitter(width = 0.2, alpha = 0.8, size = 0.5) +
  geom_lv(k = 4, outlier.shape = NA) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = method)) +
  geom_text(data = . %>% group_by(method) %>% summarise(median = median(diff)) %>% ungroup(), 
            aes(x = method, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 4) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 4), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute effect in fractional savings", 
       title = "Absolute effect of non-routine events when using different M&V methods", 
       subtitle = str_glue("All {A_building} buildings wither measured weather")) +
  coord_cartesian(ylim = c(0, 23)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))
```

```{r meancont, fig.cap="Comparison of different sampling ratio impact on M&V estimation accuracy (expressed without absolute calculation for errors)", fig.height=8, fig.width=12}

@@

p_top <- df_MW_A %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_jitter(width = 0.2, alpha = 0.8, size = 0.5) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75, linewidth = 0.15) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 4) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather conditions")) +
  coord_cartesian(ylim = c(-12, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        axis.text.x = element_blank(), 
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

@@

p_bottom <- df_TW_A %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_jitter(width = 0.2, alpha = 0.8, size = 0.5) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75, linewidth = 0.15) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 4) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with TOWT model and TMY weather")) +
  coord_cartesian(ylim = c(-12, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

@@

```{r absint2y, fig.cap="Comparison of different sampling interval impact on M&V estimation accuracy over the course of two years (dropped: all non-consecutive days were dropped; kept: all measurements were kept)", fig.height=9, fig.width=12}
# dropped version
df_interval_keep_stable %<>% 
  left_join(df_fs_stable %>% filter(method == "rand"), by = c("name", "site")) %>% 
  select(-c("scenario", "method")) %>% 
  rename("interval_fs_1" = "savings") %>% 
  left_join(df_fs_tmy_stable, by = c("name", "site")) %>% 
  select(-conv) %>% 
  rename("interval_tmy_1" = "rand")

@@

```{r meanint2y, fig.cap="Comparison of different sampling interval impact on M&V estimation accuracy over the course of the two years (without absolute calculation)", fig.width=12, fig.height=9}
# dropped version
df_drop <- df_interval_drop_stable %>% 
  bind_rows(df_interval_drop_variable) %>% 
  select(name, contains("fs")) %>% 
  rename("drop_1" = "interval_fs_1", 
         "drop_2" = "interval_fs_2", 
         "drop_3" = "interval_fs_3", 
         "drop_7" = "interval_fs_7")

>>>>

# stable dataset
readfile_stable <- str_glue("../readfiles/stable/")
fig_path = "../figs/supplementary/"

@@

```{r stablesite, fig.cap = "Site summary of the filtered buildings from BDG2 dataset (counts < 10 are omitted for visualization; left: aggregated counts of buildings for each type; right: breakdown building counts for each building type at each location)", fig.width=8, fig.height=6}

set3 <- colorRampPalette(brewer.pal('Set3',n=12))
type_colors <- setNames(set3(13), all_types_variable$type)

stable_set <- df_energy_stable %>%
  group_by(type) %>%
  distinct(name) %>%
  summarise(stable = n()) %>%
  ungroup()

variable_set <- df_energy_variable %>%
  group_by(type) %>%
  distinct(name) %>%
  summarise(variable = n()) %>%
  ungroup()

p1 <- variable_set %>% 
  left_join(stable_set, by = "type") %>% 
  mutate(stable = replace_na(stable, 0)) %>% 
  group_by(type) %>% 
  summarise(n = stable + variable) %>% 
  ungroup() %>% 
  mutate(type = fct_reorder(type, n, .desc = F)) %>%
  ggplot(aes(x = 1, y = n, fill = as.factor(type))) +
  geom_col() +
  geom_text(aes(label = ifelse(n > 10, n, "")), color = "black", position = position_stack(vjust = 0.5)) +
  scale_y_continuous(expand = c(0, 0),
                     breaks = breaks_pretty(n = 4)) +
  scale_x_discrete(expand = c(0, 0.1)) +
  scale_fill_manual(values = type_colors) +
  labs(x = NULL,
       y = NULL,
       subtitle = "Combining all",
       fill = NULL) +
  theme(axis.text.x = element_blank(),
        panel.grid.major.y = element_line(color = "grey80"),
        legend.direction = "horizontal",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

stable_set <- df_energy_stable %>% 
  left_join(df_loc, by = "site") %>% 
  group_by(type, location) %>%
  distinct(name) %>%
  summarise(stable = n()) %>%
  ungroup()

variable_set <- df_energy_variable %>% 
   left_join(df_loc, by = "site") %>% 
  group_by(type, location) %>%
  distinct(name) %>%
  summarise(variable = n()) %>%
  ungroup()

p2 <- variable_set %>% 
  left_join(stable_set, by = c("type", "location")) %>% 
  mutate(stable = replace_na(stable, 0)) %>% 
  group_by(location, type) %>% 
  summarise(n = stable + variable) %>% 
  ungroup() %>% 
  group_by(location) %>%
  mutate(proportion = n / sum(n),
         total = sum(n),
         ymax = cumsum(proportion),
         ymin = c(0, head(ymax, n = -1))) %>%
  mutate(label_pos = (ymax + ymin) / 2) %>%
  ungroup() %>%
  group_by(type) %>%
  mutate(order = sum(n)) %>%
  ungroup() %>%
  mutate(type = fct_reorder(type, order, .desc = F)) %>%
  ggplot(aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3.2, fill = type)) +
  geom_rect() +
  coord_polar(theta = "y") +
  xlim(c(2, 4)) +
  facet_wrap(~ location, nrow = 3) +
  labs(x = NULL,
       y = NULL,
       subtitle = "For each location",
       fill = NULL) +
  scale_fill_manual(values = type_colors) +
  geom_text(aes(x = 3.7, y = label_pos, label = ifelse(n > 10, n, ""))) +
  geom_text(aes(x = 2, y = 0, label = paste0("Total\n", total)), color = "black", check_overlap = T) +
  theme(legend.direction = "horizontal",
        axis.text = element_blank(),
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

ggarrange(p1, p2,
          ncol = 2, nrow = 1,
          widths = c(0.2, 1),
          common.legend = TRUE,
          legend = "bottom") +
  plot_annotation(title = "Summary of filtered buildings and types")
```

```{r chwst, fig.cap = "Proposed intervention strategy: chilled water supply temperature reset based on outdoor temperature.", fig.width=8, fig.height=4}

data.frame(
  OAT = c(10, 15, 25, 30),  
  Baseline = c(6, 6, 6, 6),      
  Intervention = c(12, 12, 7, 7)
  ) %>% 
  pivot_longer(cols = c("Baseline", "Intervention"), names_to = "strategy", values_to = "value") %>% 
  ggplot(aes(x = OAT, y = value, color = strategy)) +
  geom_line(linewidth = 1.2) +
  scale_color_manual(values = ls_colors) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = c(4, 6, 8, 10, 12),
                     limits = c(5, 12.5),
                     labels = number_format(suffix = " °C")) +
  scale_x_continuous(expand = c(0, 0), 
                     breaks = c(5, 10, 15, 20, 25, 30), 
                     labels = number_format(suffix = " °C")) +
  geom_vline(xintercept = 10, lty = "dashed", color = "red") +
  annotate(geom = "text", x = 7.5, y = 8, label = "No chiller\noperation\nbelow 10 °C", size = 5) +
  coord_cartesian(xlim = c(5, 30)) +
  labs(x = "Outdoor temperature", 
       y = "Chilled water supply temperature", 
       color = NULL, 
       title = "Chilled water supply temperature reset intervention") +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.direction = "horizontal",
        legend.position = "bottom",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

```{r meanerr, fig.cap="Distribution of estimated deviation from the ground-truth savings calculated by the two M&V methods (red dashed line highlighting 0% error)", fig.height=7, fig.width=9}
# plot for the stable subset
rand_eob_S <- df_seq_fs_stable %>% 
  filter(seq == "eob") %>% 
  left_join(df_fs_stable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = savings - fs, 
         method = "rand_eob") %>% 
  select(name, method, diff)

conv_S <- df_fs_stable %>% 
  filter(method != "rand") %>% 
  pivot_wider(names_from = method, values_from = savings) %>% 
  mutate(diff = true - conv, 
         method = "conv") %>% 
  select(name, method, diff)

rand_final_S <- df_fs_stable %>% 
  filter(method != "conv") %>% 
  pivot_wider(names_from = method, values_from = savings) %>% 
  mutate(diff = true - rand, 
         method = "rand_final") %>% 
  select(name, method, diff)

# plot for the variable subset
rand_eob_V <- df_seq_fs_variable %>% 
  filter(seq == "eob") %>% 
  left_join(df_fs_variable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site"))%>% 
  mutate(diff = savings - fs, 
         method = "rand_eob") %>% 
  select(name, method, diff)

conv_V <- df_fs_variable %>% 
  filter(method != "rand") %>% 
  pivot_wider(names_from = method, values_from = savings) %>% 
  mutate(diff = true - conv, 
         method = "conv") %>% 
  select(name, method, diff)

rand_final_V <- df_fs_variable %>% 
  filter(method != "conv") %>% 
  pivot_wider(names_from = method, values_from = savings) %>% 
  mutate(diff = true - rand, 
         method = "rand_final") %>% 
  select(name, method, diff)

p_top <- df_MW_A %>% 
  mutate(method = as.factor(method), 
         method = recode_factor(method, "conv_diff" = "Conventional", "rand_eob_diff" = "Randomized", "rand_final_diff" = "Randomized\n(24 months)")) %>% 
  ggplot(aes(x = method, y = diff, fill = method)) +
  geom_lv(k = 4, outlier.shape = NA) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = method), linewidth = 0.25) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1.5, lty = "dashed") +
  geom_text(data = . %>% group_by(method) %>% summarise(median = median(diff)) %>% ungroup(), 
            aes(x = method, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       color = NULL, 
       x = NULL, 
       y = "Estimated error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather")) +
  coord_cartesian(ylim = c(-15, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        axis.text.x = element_blank(),
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

# TMY
# plot for the stable subset
rand_eob_S <- df_sprt_all_stable %>% 
  filter(seq == "eob") %>% 
  select(-c(seq, n_weeks)) %>% 
  left_join(df_fs_stable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = savings - annual, 
         method = "rand_eob") %>% 
  select(name, method, diff)

conv_S <- df_fs_tmy_stable %>% 
  left_join(df_fs_stable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = savings - conv, 
         method = "conv") %>% 
  select(name, method, diff)

rand_final_S <- df_fs_tmy_stable %>% 
  left_join(df_fs_stable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = savings - rand, 
         method = "rand_final") %>% 
  select(name, method, diff)

df_TW_S <- rbind(rand_eob_S, conv_S, rand_final_S)

# plot for the variable subset
rand_eob_V <- df_sprt_all_variable %>% 
  filter(seq == "eob") %>% 
  select(-c(seq, n_weeks)) %>% 
  left_join(df_fs_variable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = savings - annual, 
         method = "rand_eob") %>% 
  select(name, method, diff)

conv_V <- df_fs_tmy_variable %>% 
  left_join(df_fs_variable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = savings - conv, 
         method = "conv") %>% 
  select(name, method, diff)

rand_final_V <- df_fs_tmy_variable %>% 
  left_join(df_fs_variable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = savings - rand, 
         method = "rand_final") %>% 
  select(name, method, diff)

df_TW_V <- rbind(rand_eob_V, conv_V, rand_final_V)

df_TW_A <- rand_eob_A %>% 
  left_join(conv_A, by = "name") %>% 
  left_join(rand_final_A, by = "name") %>% 
  pivot_longer(c(rand_eob_diff, conv_diff, rand_final_diff), names_to = "method", values_to = "diff")

p_middle <- df_TW_A %>% 
  mutate(method = as.factor(method), 
         method = recode_factor(method, "conv_diff" = "Conventional", "rand_eob_diff" = "Randomized", "rand_final_diff" = "Randomized\n(24 months)")) %>% 
  ggplot(aes(x = method, y = diff, fill = method)) +
  geom_lv(k = 4, outlier.shape = NA) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = method), linewidth = 0.25) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1.5, lty = "dashed") +
  geom_text(data = . %>% group_by(method) %>% summarise(median = median(diff)) %>% ungroup(), 
            aes(x = method, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Estimated error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with TOWT model and TMY weather")) +
  coord_cartesian(ylim = c(-15, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

ggarrange(p_top, p_middle, 
          ncol = 1, nrow = 2,
          labels = c("a)", "b)")) +
  plot_annotation(title = "Estimated error in savings estimation by different M&V methods")

percentiles <- df_TW_A %>%
  filter(method == "conv_diff") %>% 
  summarise(
    Q1     = round(quantile(diff, 0.25, na.rm = TRUE), digits = 2),
    Median = round(quantile(diff, 0.50, na.rm = TRUE), digits = 2),
    Q3     = round(quantile(diff, 0.75, na.rm = TRUE), digits = 2)
  )
```

```{r absnull, fig.cap="Comparison between the two M&V methods in detecting no intervention effect (expressed without absolute calculation) when buildings are subject to baseline change.", fig.height=4, fig.width=9}
#### ABS-NULL ####
rand_eob_S <- df_seq_fs_null_stable %>% 
  filter(seq == "eob") %>% 
  mutate(diff = abs(0 - fs), 
         method = "rand_eob") %>% 
  select(name, method, diff)

@@

df_MW_A %>% 
  mutate(method = as.factor(method), 
         method = recode_factor(method, "conv_diff" = "Conventional", "rand_eob_diff" = "Randomized", "rand_final_diff" = "Randomized\n(24 months)")) %>% 
  ggplot(aes(x = method, y = diff, fill = method)) +
  geom_lv(k = 4, outlier.shape = NA) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = method)) +
  geom_text(data = . %>% group_by(method) %>% summarise(median = median(diff)) %>% ungroup(), 
            aes(x = method, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 4), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute effect in fractional savings", 
       title = "Estimated absolute effect of non-routine events by different M&V methods", 
       subtitle = str_glue("All {A_building} buildings wither measured weather")) +
  coord_cartesian(ylim = c(0, 23)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))
```

```{r meancont, fig.cap="Comparison of different sampling ratio impact on M&V estimation accuracy (expressed without absolute calculation for errors)", fig.height=7, fig.width=9}

@@

p_top <- df_MW_A %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75, linewidth = 0.15) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather conditions")) +
  coord_cartesian(ylim = c(-12, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        axis.text.x = element_blank(), 
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

@@

p_bottom <- df_TW_A %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75, linewidth = 0.15) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with TOWT model and TMY weather")) +
  coord_cartesian(ylim = c(-12, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

@@

```{r abscont, fig.cap="Comparison of different sampling ratio impact on M&V estimation accuracy over the entire 24 months (previous results of sampling at 50%/50% shown on the left side of the red dashed line)", fig.height=7, fig.width=9}

#### ABS-CONT ####
df_MW_S <- df_cont_stable %>% 
  left_join(df_fs_stable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = abs(savings - cont_fs), 
         diff_all = abs(savings - cont_fs_all)) %>% 
  select(name, diff, diff_all, ratio) %>% 
  pivot_longer(c(diff, diff_all), names_to = "type", values_to = "values") %>% 
  mutate(ratio = ifelse(ratio == 1 & type == "diff", "1_1", 
                        ifelse(ratio == 1 & type == "diff_all", "1_2", 
                               ifelse(ratio == 2 & type == "diff", "2_1", 
                                      ifelse(ratio == 2 & type == "diff_all", "2_2", ratio))))) %>% 
  bind_rows(df_fs_stable %>% 
              filter(method != "conv") %>% 
              pivot_wider(names_from = method, values_from = savings) %>% 
              mutate(values = abs(true - rand), 
                     ratio = "0", 
                     type = "diff_ref") %>% 
              select(name, values, ratio, type))

# plot for the variable subset
df_MW_V <- df_cont_variable %>% 
  left_join(df_fs_variable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = abs(savings - cont_fs), 
         diff_all = abs(savings - cont_fs_all)) %>% 
  select(name, diff, diff_all, ratio) %>% 
  pivot_longer(c(diff, diff_all), names_to = "type", values_to = "values") %>% 
  mutate(ratio = ifelse(ratio == 1 & type == "diff", "1_1", 
                        ifelse(ratio == 1 & type == "diff_all", "1_2", 
                               ifelse(ratio == 2 & type == "diff", "2_1", 
                                      ifelse(ratio == 2 & type == "diff_all", "2_2", ratio))))) %>% 
  bind_rows(df_fs_variable %>% 
              filter(method != "conv") %>% 
              pivot_wider(names_from = method, values_from = savings) %>% 
              mutate(values = abs(true - rand), 
                     ratio = "0", 
                     type = "diff_ref") %>% 
              select(name, values, ratio, type))

p_top <- df_MW_A %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 4), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather conditions")) +
  coord_cartesian(ylim = c(0, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        axis.text.x = element_blank(), 
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

# TMY
# plot for the stable subset
df_TW_S <- df_cont_stable %>% 
  left_join(df_fs_stable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = abs(savings - cont_tmy), 
         diff_all = abs(savings - cont_tmy_all)) %>% 
  select(name, diff, diff_all, ratio) %>% 
  pivot_longer(c(diff, diff_all), names_to = "type", values_to = "values") %>% 
  mutate(ratio = ifelse(ratio == 1 & type == "diff", "1_1", 
                        ifelse(ratio == 1 & type == "diff_all", "1_2", 
                               ifelse(ratio == 2 & type == "diff", "2_1", 
                                      ifelse(ratio == 2 & type == "diff_all", "2_2", ratio))))) %>% 
  bind_rows(df_fs_tmy_stable %>% 
              left_join(df_fs_stable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
              mutate(values = abs(savings - rand), 
                     ratio = "0", 
                     type = "diff_ref") %>% 
              select(name, values, ratio, type))

# plot for the variable subset
df_TW_V <- df_cont_variable %>% 
  left_join(df_fs_variable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = abs(savings - cont_tmy), 
         diff_all = abs(savings - cont_tmy_all)) %>% 
  select(name, diff, diff_all, ratio) %>% 
  pivot_longer(c(diff, diff_all), names_to = "type", values_to = "values") %>% 
  mutate(ratio = ifelse(ratio == 1 & type == "diff", "1_1", 
                        ifelse(ratio == 1 & type == "diff_all", "1_2", 
                               ifelse(ratio == 2 & type == "diff", "2_1", 
                                      ifelse(ratio == 2 & type == "diff_all", "2_2", ratio))))) %>% 
  bind_rows(df_fs_tmy_variable %>% 
              left_join(df_fs_variable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
              mutate(values = abs(savings - rand), 
                     ratio = "0", 
                     type = "diff_ref") %>% 
              select(name, values, ratio, type))

p_bottom <- df_TW_A %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 4), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with TOWT model and TMY weather")) +
  coord_cartesian(ylim = c(0, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

```{r absint2y, fig.cap="Comparison of different sampling interval impact on M&V estimation accuracy over the course of two years (dropped: all non-consecutive days were dropped; kept: all measurements were kept)", fig.height=8, fig.width=9}
# dropped version
df_interval_keep_stable %<>% 
  left_join(df_fs_stable %>% filter(method == "rand"), by = c("name", "site")) %>% 
  select(-c("scenario", "method")) %>% 
  rename("interval_fs_1" = "savings") %>% 
  left_join(df_fs_tmy_stable, by = c("name", "site")) %>% 
  select(-conv) %>% 
  rename("interval_tmy_1" = "rand")

@@

```{r meanint2y, fig.cap="Comparison of different sampling interval impact on M&V estimation accuracy over the course of the two years (without absolute calculation)", fig.width=9, fig.height=8}
# dropped version
df_drop <- df_interval_drop_stable %>% 
  bind_rows(df_interval_drop_variable) %>% 
  select(name, contains("fs")) %>% 
  rename("drop_1" = "interval_fs_1", 
         "drop_2" = "interval_fs_2", 
         "drop_3" = "interval_fs_3", 
         "drop_7" = "interval_fs_7")
